Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-05 Paper/paperN.tex
slight mod in who did what and some sentences rephrased

\begin{table}
\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
  \hline
  \textit{frame predicate} & \textit{verbs in frame}\\
  \hline
  \hline
  knowledge transfer & explain, assure, arrange, acquaint\\
  \hline
  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
  \hline
  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
  \hline
  affection & love, hate\\
  \hline
  harming anotherly &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
  \hline
  enjoyment & enjoy, please, bow, amount\\
  \hline
\end{tabular}
\label{exframes}
\caption{Frame examples}
\end{table}

\section{Discussion}
As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much. But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are assigned to a frame. It is not clear why this happens, but this are still only experimental results.  Since there are 200 frames it is obvious that the coherency is so low. Other experiments have shown that it is possible to cluster with model 0 though.

The frames in table \ref{exframes} are frames induced by model 1 and are meaningful in the sense that they consist of clusters of verbs that seem to have a similar meaning. Nonetheless, in \textit{harming anotherly} there are verbs which would be better left out. They are assigned this frame though because they occurred in company of the same arguments often. The affection frame is remarkable since these are exactly opposites. This happens in some form in more frames though and can be explained by the fact that verbs with opposite meanings are used with the same arguments, this can be seen as a weakness of the model.

Furthermore auxiliary verbs get mostly assigned a complete frame, i.e. they are the only verb assigned to a frame. Other verbs like \textit{(say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find)} also get assigned a complete frame. This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb by nouns it is encountered with, sort of meaningless. This is again a weakness of the model, but could possibly be diminished with more data.

@@

\section*{Who did what}
We all tried to work as much as possible and necessary on the project. Bill had a leading role in building the models. Model 1 is completely build and implemented by Bill. Jacob implemented frame coherency and Eli frame correctness. Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid-search). Any section is written by the one who implemented this particular part. The rest of the sections are composed of bits of everybody.

>>>>

\begin{table}
\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
  \hline
  \textit{frame predicate} & \textit{verbs in frame}\\
  \hline
  \hline
  knowledge transfer & explain, assure, arrange, acquaint\\
  \hline
  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
  \hline
  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
  \hline
  affection & love, hate\\
  \hline
  harming anotherly &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
  \hline
  enjoyment & enjoy, please, bow, amount\\
  \hline
\end{tabular}
\caption{Frame examples}
\label{exframes}
\end{table}

\section{Discussion}
As table \ref{results} shows, coherency  improved significantly, whereas the frame correctness did not so much. But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are assigned to a frame. It is not clear why this happens, but this are still only experimental results.  Since there are 200 frames it is obvious that the coherency is so low. Other experiments have shown that it is possible to cluster with model 0 though.

Table \ref{exframes} showes some frames induced by model 1 and are meaningful in the sense that they primarily consist of clusters of verbs that seem to have a similar meaning. Nonetheless, in \textit{harming anotherly} there are verbs which would be better left out. They are assigned this frame though because they occurred in company of the same arguments often. The affection frame is remarkable since these are exactly opposites. This happens in some form in more frames though and can be explained by the fact that verbs with opposite meanings are used with the same arguments, this can be seen as a weakness of the model.

Furthermore auxiliary verbs get mostly assigned a complete frame, i.e. they are the only verb assigned to a frame. Other verbs like \textit{say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find} also get assigned a complete frame. This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb-by-nouns-it-is-encountered-with, sort of meaningless. This is again a weakness of the model, but could possibly be diminished with more data.

@@

\section*{Who did what}
We all tried to work as much as possible and necessary on the project. Bill had a leading role in building the models. Model 1 is completely build and implemented by Bill. Jacob implemented frame coherency and Eli frame correctness. Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid-search). Any section is written by the one who implemented this particular part. The rest of the sections are composed of bits of everybody, but most important and precise work is done by Bill.
